An Automatic Verification Framework for Software Configurations

### 2016-05-02 OSDI/abs.tex
config: new abs

System failures resulting from configuration errors 
have become the major factors affecting the availability and
reliability of today's software systems.
While many misconfiguration handling techniques,
\eg, misconfiguration checking and troubleshooting, have been proposed, 
offering automatic verification to configuration files -- like
what we did to regular programs -- is still an open problem.
The main reason is software configuration files are poorly structured 
and typed, thus obstructing any possible language-based verification. 
This paper presents, \app, the first automatic verification framework for
software configurations.
In order to verify a configuration file,
\app first analyzes a given dataset sample of configuration files, 
and then derives rules for building a language model from 
the given configuration dataset. 
Finally, the resulting language model can be used
to verify new configuration files and detect errors in them.
At the heart of \app lies a novel learning engine, 
which employs a probabilistic type inference strategy and
defines an intermediate representation for the rule type.
Using this engine, \app learns various type rules (\eg, orderings,
value relations, type errors, and user defined rules)
to verify configuration files of interest.
\app framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results.}

>>>>

System failures resulting from configuration errors 
have become the major causes affecting the availability and
reliability of today's software systems.
While many misconfiguration handling techniques,
\eg, misconfiguration checking, troubleshooting and repair, 
have been proposed, 
offering automatic verification for configuration files -- like
what we did to regular programs -- is still an open problem.
This is because 1) software configurations are typically written in
poorly structured and untyped representations, and 2) 
writing specifications or constraints for configuration 
verification is non-trivial.
This paper presents, \app, the first automatic verification framework for
software configurations.
For a given configuration file,
\app first analyzes a dataset sample of configuration files,
thus generating a well-structured and probabilistically-typed 
intermediate representations.
Then, \app derives rules and constraints by analyzing
the intermediate representations.
The above two steps have formulated a language model.
Finally, the resulting language model can be used
to verify the given configuration file and capable of 
detecting various tricky errors,
including orderings, value correlation, type errors, and entry missing.
%At the heart of \app lies a novel learning engine, 
%which employs a probabilistic type inference strategy and
%defines an intermediate representation for the rule type.
%With this engine, \app learns various type rules (\eg, orderings,
%value relations, type errors, and user defined rules)
%to verify configuration files of interest.
Our \app framework is highly modular, 
does not rely on the system source code, and
can be applied to any new configuration file type with minimal user input.  
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results. For example, we verify real-world misconfiguration 
files and find 95\% errors are detected.}

### 2016-05-02 OSDI/intro.tex
config: new abs

Configuration errors are one of the most important root-causes of
modern software system failures~\cite{xu15systems,yin11anempirical}.
In practice, misconfiguration problems may result in security
vulnerabilities, application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.  Although several
tools have been proposed to automate configuration error diagnosis
after failures occur~\cite{wang04automatic,attariyan10automating,
su07autobash,whitaker04configuration}, these tools rely on a manual approach
  to understand and detect the failure symptoms. The main reasons for this are:
  1) entries in configuration files are untyped assignments, 2) there
  is no explicit structure policy for the entries in configuration
  files, and 3) there are surprisingly few rules specifying the
  entries' constraints.

>>>>

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
In practice, misconfiguration problems may lead to security
vulnerabilities, application crashes, severe disruptions in software
functionality, and incorrect program executions%
~\cite{zhang14encore, yuan11context, xu13do, xu15hey}.  
Although many efforts tackling misconfigurations have been proposed 
to check, troubleshoot, diagnose and repair configuration errors%
~\cite{wang04automatic, attariyan10automating,
su07autobash, whitaker04configuration}, these efforts rely on a manual 
approach to understand and detect the failure symptoms. 
The main reasons for this are:
1) entries in configuration files are untyped assignments, 2) there
is no explicit structure policy for the entries in configuration
files, and 3) there are surprisingly few rules specifying the
entries' constraints.

Verifying configuration files have been advocated as a reasonable means
to check the correctness of configuration files of interest.
